A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-14 paper.tex
slim down abstract to reduce page num to 25

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{2} \and
Andre Kuhlenschmidt\inst{2}
}
%
\authorrunning{Lu et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Brown University, Providence RI 02912, USA \and
Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
% Background
Gradual typing combines dynamic typing and static typing in one
language to provide the advantages of both typing
disciplines. Implementing gradual typing with reasonable overhead,
however, is not trivial. Casts accumulate on higher-order values and
continuations, changing the overall space complexity. Several
space-efficient cast representations have been proposed, notably
coercions in normal forms and threesomes.
These cast representations shall be proved not changing the overall
behavior of language implementations except saving space.
Existing proofs typically go through a bisimulation between
a space-efficient semantics, which use a specific cast representation,
and the definitional but inefficient semantics \citep{Siek:2010:TWB:1706299.1706342,Siek:2015:BCT:2737924.2737968}.
% Problem
This technique imposes unnecessary burden in proving such theorems
because a considerable portion of the semantics is irrelevant to
casts.
% Solution
To isolate cast representations from the remaining part of 
semantics, we present a abstract data type, namely Cast ADT,
that captures interface functions a cast representations typically 
includes, and an abstract machine parameterized over Cast ADTs.
Our generic dynamic semantics comes with generic theorems,
% Why is our solution a step forward
with which the correctness proofs can be done by just proving 
properties of a specific Cast ADT.
% %
% To isolate cast representations from the remaining part of 
% implementations, we present a abstract data type, namely Cast ADT,
% that captures interface functions a cast representations typically 
% includes, and an abstract machine parameterized over Cast ADTs.
% %
% With our generic abstract machine, the correctness proofs can be
% done by proving properties of a specific Cast ADT, which is simpler
% than proofs regarding the entire dynamic semantics.
%%%%%
% %
% But they are presented in
% different dynamic semantics, which make it difficult to compare the
% key differences between the cast representations.
% %
% We present a
% abstract data type, namely Cast ADT, that captures interface functions
% a cast representations typically includes, and an abstract machine
% parameterized over Cast ADTs.
% %
% The Cast ADT brings another benefit:
% space-efficient cast representations shall be proved not changing the
% overall behavior of language implementations except saving space.
% %
% With our generic abstract machine, these proofs can be done by proving
% properties of a specific Cast ADT, which is simpler than proofs
% regarding the entire dynamic semantics.
\todo[inline]{JS: The stuff above about ``make it difficult to compare''
  is a weak argument. I would recommend deleting that argument and
  instead focus on the benefits regarding the proofs of correctness.}
\todo[inline]{KC: updated.}

@@

Lemma~\ref{lem:weak-bisimulation} is proved by case analysis on \bisims{s_1}{s_1'}{T}.
Function call is the most interesting case. In this case the function value in
\CMachine{B}
must be of the form 
\[
v_1 = \vfuncc{
		\vfuncc{
			\vfunc{x}{S_1}{e}{E}
		}{S_1}{T_1}{l_1}{S_2}{T_2}
		\ldots
	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
\]
By induction of the sequence of casts, we know \scont{v_2}{\Kcons{\FappOX{v_1}}{K}} will
transition to
\[
\begin{array}{l}
\mlet{v_2}{\applyCast{v_2}{\ccast{S_n}{\bar{l}}{S_{n-1}}}}{} \\
\ldots \\
\mlet{v_2}{\applyCast{v_2}{\ccast{S_2}{\bar{l}}{S_1}}}{} \\
\sexpr{e}{E[x:=v_2]}{
	\Kcons{\Fcast{\ccast{T_1}{l}{T_2}}}{
	    \ldots
	    \Kcons{\Fcast{\ccast{T_{n-1}}{l}{T_n}}}{K}}
}
\end{array}
\]
% Assuming \bisimv{v_1}{v_1'}{\Pfunc{S_n}{T_n}} and \bisimv{v_2}{v_2'}{S_n}.
As for \SMachine{C}, the function value must be of the form
\[
v_1' = \ecast{\vfunc{x}{S}{e}{E'}}{\Pfunc{c}{d}}
\]
where
\[
\begin{array}{l}
\bisimc{(\ccast{S_n}{\bar{l}}{S_{n-1}} \ldots \ccast{S_2}{\bar{l}}{S_1})}{c}{S_n}{S_1} \\
\bisimc{(\ccast{T_1}{l}{T_1} \ldots \ccast{T_{n-1}}{l}{T_n})}{d}{T_1}{T_n} \\
\end{array}
\]
By the definition of \applyContName\ we know \applyCont{v_2'}{\Kcons{\FappOX{v_1'}}{K}} will
transition to
\[
\begin{array}{l}
\mlet{v_2'}{\denote{c}(v_2')}{} \\
\sexpr{e}{E'[x:=v_2']}{\extCont{d}{K'}}
\end{array}
\]
Intuitively, we need to show the sequence of let bindings in \CMachine{B}
bisimulate the single let binding in \SMachine{C}, and that the two 
extended continuations bisimulate. Both of them are straightforward to
proof.

>>>>

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{2} \and
Andre Kuhlenschmidt\inst{2}
}
%
\authorrunning{Lu et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Brown University, Providence RI 02912, USA \and
Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
% Background
Gradual typing combines dynamic typing and static typing in one
language to provide the advantages of both typing
disciplines. Implementing gradual typing with reasonable overhead,
however, is not trivial. Casts accumulate on higher-order values and
continuations, changing the overall space complexity. Several
space-efficient cast representations have been proposed, notably
coercions in normal forms and threesomes.
A correct cast representations shall be proved not changing the overall
behavior of language implementations except saving space.
Existing proofs typically go through a bisimulation between
the language semantics and a space-efficient one 
\citep{Siek:2010:TWB:1706299.1706342,Siek:2015:BCT:2737924.2737968}.
% Problem
The similarity of these proofs suggests that people should be able
to prove correctness for a cast representation by proving it holds
certain properties.
% Solution
We present an abstract data type, namely Cast ADT,
that captures interface functions a cast representations typically 
provides, and an abstract machine parameterized over Cast ADTs.
Our abstract machine comes with generic theorems,
% Why is our solution a step forward
with which the correctness proofs can be done by just proving 
properties of a specific Cast ADT.
% %
% To isolate cast representations from the remaining part of 
% implementations, we present a abstract data type, namely Cast ADT,
% that captures interface functions a cast representations typically 
% includes, and an abstract machine parameterized over Cast ADTs.
% %
% With our generic abstract machine, the correctness proofs can be
% done by proving properties of a specific Cast ADT, which is simpler
% than proofs regarding the entire dynamic semantics.
%%%%%
% %
% But they are presented in
% different dynamic semantics, which make it difficult to compare the
% key differences between the cast representations.
% %
% We present a
% abstract data type, namely Cast ADT, that captures interface functions
% a cast representations typically includes, and an abstract machine
% parameterized over Cast ADTs.
% %
% The Cast ADT brings another benefit:
% space-efficient cast representations shall be proved not changing the
% overall behavior of language implementations except saving space.
% %
% With our generic abstract machine, these proofs can be done by proving
% properties of a specific Cast ADT, which is simpler than proofs
% regarding the entire dynamic semantics.
\todo[inline]{JS: The stuff above about ``make it difficult to compare''
  is a weak argument. I would recommend deleting that argument and
  instead focus on the benefits regarding the proofs of correctness.}
\todo[inline]{KC: updated.}

@@

Lemma~\ref{lem:weak-bisimulation} is proved by case analysis on \bisims{s_1}{s_1'}{T}.
Function call is the most interesting case. In this case the function value in
\CMachine{B}
must be of the form 
\[
v_1 = \vfuncc{
		\vfuncc{
			\vfunc{x}{S_1}{e}{E}
		}{S_1}{T_1}{l_1}{S_2}{T_2}
		\ldots
	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
\]
By induction of the sequence of casts, we know \scont{v_2}{\Kcons{\FappOX{v_1}}{K}} will
transition to
\[
\begin{array}{l}
\mlet{v_2}{\applyCast{v_2}{\ccast{S_n}{\bar{l}}{S_{n-1}}}}{} \\
\ldots \\
\mlet{v_2}{\applyCast{v_2}{\ccast{S_2}{\bar{l}}{S_1}}}{} \\
\sexpr{e}{E[x:=v_2]}{
	\Kcons{\Fcast{\ccast{T_1}{l}{T_2}}}{
	    \ldots
	    \Kcons{\Fcast{\ccast{T_{n-1}}{l}{T_n}}}{K}}
}
\end{array}
\]
% Assuming \bisimv{v_1}{v_1'}{\Pfunc{S_n}{T_n}} and \bisimv{v_2}{v_2'}{S_n}.
As for \SMachine{C}, the function value must be of the form
\[
v_1' = \ecast{\vfunc{x}{S}{e}{E'}}{\Pfunc{c}{d}}
\]
where
\[
\begin{array}{l}
\bisimc{(\ccast{S_n}{\bar{l}}{S_{n-1}} \ldots \ccast{S_2}{\bar{l}}{S_1})}{c}{S_n}{S_1} \\
\bisimc{(\ccast{T_1}{l}{T_1} \ldots \ccast{T_{n-1}}{l}{T_n})}{d}{T_1}{T_n} \\
\end{array}
\]
By the definition of \applyContName\ we know \applyCont{v_2'}{\Kcons{\FappOX{v_1'}}{K}} will
transition to
\[
\begin{array}{l}
\mlet{v_2'}{\denote{c}(v_2')}{} \\
\sexpr{e}{E'[x:=v_2']}{\extCont{d}{K'}}
\end{array}
\]
Intuitively, we need to show the sequence of let bindings in \CMachine{B}
bisimulate the single let binding in \SMachine{C}, and that the two 
extended continuations bisimulate each other. The first part follows from
